Constraint Programming - Inside Gecode

### 2014-05-03 paper.tex
constraint propagation search tree

		\node[rectangle,draw] at (-3.6, 1) (levelThreeElementOne) {$y = 1$};
		\coordinate[left=0.2cm of levelTwoElementOne.south] (levelTwoElementOnePointOne);
  		\path[arrow] (levelThreeElementOne) -- (levelTwoElementOnePointOne);
		\node[rectangle,draw] at (-3.6, 0) (levelFourElementOne) {$c_2 \lightning$};
  		\path[arrow] (levelFourElementOne) -- (levelThreeElementOne);
		\node[rectangle,draw] at (-2.4, 1) (levelThreeElementTwo) {$y = 2$};
		\coordinate[right=0.2cm of levelTwoElementOne.south] (levelTwoElementOnePointTwo);
  		\path[arrow] (levelThreeElementTwo) -- (levelTwoElementOnePointTwo);
		\node[rectangle,draw] at (-2.4, 0) (levelFourElementTwo) {\Checkmark};
  		\path[arrow] (levelFourElementTwo) -- (levelThreeElementTwo);

@@

	To visualize this effect consider a constraint problem based on two variables $x \in \{1, 5, 6\}$ and $y \in \{1, 2\}$ and two constraints based on them.
	\begin{equation}
		c_1:\ x \le y
	\end{equation}
	\begin{equation}
		c_2:\ x + y = 3
	\end{equation}
	Without constraint propagation and branching first on $x$ this results in search tree \reffig{fig:bigTree}.

>>>>

		\node[rectangle,draw] at (-3.6, 1) (levelThreeElementOne) {$y = 1$};
		\coordinate[left=0.2cm of levelTwoElementOne.south] (levelTwoElementOnePointOne);
  		\path[arrow] (levelThreeElementOne) -- (levelTwoElementOnePointOne);
		\node[rectangle,draw] at (-3.6, 0) (levelFourElementOne) {\Checkmark};
  		\path[arrow] (levelFourElementOne) -- (levelThreeElementOne);
		\node[rectangle,draw] at (-2.4, 1) (levelThreeElementTwo) {$y = 2$};
		\coordinate[right=0.2cm of levelTwoElementOne.south] (levelTwoElementOnePointTwo);
  		\path[arrow] (levelThreeElementTwo) -- (levelTwoElementOnePointTwo);
		\node[rectangle,draw] at (-2.4, 0) (levelFourElementTwo) {\Checkmark};
  		\path[arrow] (levelFourElementTwo) -- (levelThreeElementTwo);

@@

	\begin{figure}
	\center
	\begin{tikzpicture}
		\tikzstyle{arrow}=[draw, -latex]
		\node[rectangle,draw] at (0, 2) (levelOne) {$x \in \{1\} \land y \in \{1, 2\}$};

		\node[rectangle,draw] at (-1, 1) (levelTwoElementOne) {$y = 1$};
		\coordinate[left=0.2cm of levelOne.south] (levelOnePointOne);
  		\path[arrow] (levelTwoElementOne) -- (levelOnePointOne);
		\node[rectangle,draw] at (-1, 0) (levelThreeElementOne) {\Checkmark};
  		\path[arrow] (levelThreeElementOne) -- (levelTwoElementOne);
		\node[rectangle,draw] at (1, 1) (levelTwoElementTwo) {$y = 2$};
		\coordinate[right=0.2cm of levelOne.south] (levelOnePointTwo);
  		\path[arrow] (levelTwoElementTwo) -- (levelOnePointTwo);
		\node[rectangle,draw] at (1, 0) (levelThreeElementTwo) {\Checkmark};
  		\path[arrow] (levelThreeElementTwo) -- (levelTwoElementTwo);
	\end{tikzpicture}
	\caption{search tree with constraint propagation}
	\label{fig:smallTree}
	\end{figure}

	To visualize this effect consider a constraint problem based on two variables $x \in \{1, 5, 6\}$ and $y \in \{1, 2\}$ and one constraint based on them.
	\begin{equation}
		c_1:\ x \le y
	\end{equation}
	Without constraint propagation and branching first on $x$ this results in search tree \reffig{fig:bigTree}. Obviously the right parts of these tree can already be pruned at the root with propagation of constraint $c_1$ and therefore it is not necessary to create and evaluate these subtrees \reffig{fig:smallTree}.
